%%%%%%%%%%%%%%%%
% This is an sample CV template.
% Author: Alois.Heloir
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

\documentclass[12pt,a4paper]{heloircv}

\name{Aloïs Heloir}
\headline{Software Engineer}

\geometry{
    a4paper,
    left=10mm,
    right=10mm,
    top=0mm,
    bottom=10mm,
    headheight=30pt,
    voffset=30pt,
    footskip=40pt
}

\homepage{heloir.dev}
\linkedin{linkedin.com/in/alois-heloir}
\github{github.com/AloisH}
\email{alois.heloir@live.fr}

\begin{document}
    \cvheader

    \cvsection{Education}{%
        \education{Epita school of engineering and computer science}{Bachelor of Science (B.Sc.) Computer Science}{2018 - 2023}
        \begin{itemize}
            \item Major in Multimedia and Information Technology
            \item Member of the student council in 2021
        \end{itemize}
    }

    \cvsection{Work Experience}{%
        \work{YAKA - Programming Assistant}{EPITA - Paris, France}{01/2022 - 07/2022}{
            \begin{itemize}
                \item Programming assistant (C++, SQL, java, JS) for more than 600 first year engineering students.
            \end{itemize}
        }

        \work{Fullstack developer}{Padoa - Paris, France}{09/2021 – 02/2022}{%
            \begin{itemize}
              \item Working on the main PADOA application which is composed of a frontend in Angular 12 and a backend in NodeJS 14 with Express and PostgreSQL
              \item \textbf{Optimization of the api}: The import and export excel could cause the backend to crash if the file was to big because it consumed too much ram. Implementation of a worker system to perform heavy tasks outside the backend
              \item \textbf{Redesign of the employee modification history system}: When modifying, merging, or adding information to an employee's record, we record the person who made the change. This involves a system of access to information, anonymization, and managing multi-company employees.
              \item \textbf{UI}: Redesign of all the filter selection interface of the angular application.
            \end{itemize}
        }

        \work{ACDC - Programming Assistant C\#, Caml}{EPITA - Paris, France}{09/2020 - 07/2021}{%
            \begin{itemize}
              \item Programming assistant (C\# - Caml language) for first year students at Epita (preparatory cycle).
              \item Creation of several exercise topics in C\# to help student learn object-oriented programming.

            \end{itemize}
        }
        \work{Web developer}{CEOS-IT - Béthune, France}{07/2020 – 08/2020}{%
            \begin{itemize}
              \item Creation of a JS application to facilitate the signature of electronic documents named Eprovy
              \item A Rest API in PHP which allows to make the link between the front application and the Universign API
            \end{itemize}
        }
        \work{Internship - Web developer}{CEOS-IT - Béthune, France}{07/2019 – 08/2019}{%
            \begin{itemize}
              \item Creation of a web application to send sms to a list of users using the OVH API
            \end{itemize}
        }
    }

    \cvsection{Projects}{%
        \begin{itemize}
            \item \textbf{\href{https://github.com/MTI-2023-TALA/StudAsso}{Stud'Asso}}: Leading a team of 4 people to create an open source web application developed in Angular and NestJS to help manage school association
            \item \textbf{Spider}: Web server in C++. Implemented Http protocol, load balancer and proxy.
            \item \textbf{42sh}: Built a shell interpreter in C, Implemented variables, function, conditionals, loops, order of operations, pipe.
            \item \textbf{ImalysRCP}: Creation of a Php application to facilitate multidisciplinary consultation meetings. Used for more than 1000 patients
            \item \textbf{\href{https://loup-d.github.io/Test/}{Pointless Adventure}}: Multiplayer video game in the Unity engine written in C\# .
            \item \textbf{\href{https://play.google.com/store/apps/details?id=com.Heloir.ProjetZombsCastle}{ZombsCastle}}: Creation of a video game on mobile, available on the Google play Store
        \end{itemize}
    }

    \cvsection{Technical skills}{%
        \tag{Javascript}
        \tag{Typescript}
        \tag{Angular}
        \tag{Html5}
        \tag{Css}
        \tag{Scss}
        \tag{PHP}
        \tag{C/C++}
        \tag{C\# Dotnet}
        \tag{Python}
        \par\smallskip
        \tag{MySql}
        \tag{PostgreSql}
        \tag{Git}
        \tag{GitHub Action}
        \tag{CircleCi}
        \tag{Docker}
        \tag{NestJs}
        \tag{NodeJs}
        \tag{Linux}
        \par\smallskip
        \tag{Windows}
        \tag{TDD}
        \tag{Agile}
        \tag{UI/UX}
    }
    \filbreak
    \cvsection{Soft Skills}{%
        \tag{French Native}
        \tag{English TOIC 975}
        \tag{Leader}
        \tag{Curious}
    }
\end{document}
